\section{\textbf{Programming Design}}
\subsection{}
\textbf{Convex Hull Algorithms:}

\textbf{0.2.1 Brute Force Convex Hull Algorithm:}

The Brute Force algorithm iteratively checks every triplet of points for a valid convex hull. This algorithm has a time
complexity of O(nˆ4) and a space complexity of O(n).
\textbf{0.2.2 Jarvis March Convex Hull Algorithm:}

Jarvis March, also known as the Gift Wrapping algorithm, selects the point with the lowest y-coordinate as the starting
point and iteratively selects the next point with the smallest polar angle. The time complexity of Jarvis March is
O(nˆ2), with a space complexity of O(n).
\textbf{0.2.3 Graham Scan Convex Hull Algorithm:}

The Graham Scan algorithm involves sorting points based on their polar angles and constructing the convex hull in a
counterclockwise manner. The time complexity of Graham Scan is O (n log n), and its space complexity is O(n).

\textbf{0.2.4 Quick Elimination Convex Hull Algorithm:}

Quick Elimination is an optimization of Graham Scan, where the point set is divided into smaller subsets, and Graham
Scan is applied to each subset. The time complexity is O (n log h), and the space complexity is O(n).

\textbf{0.2.5 Andrew’s Monotone Chain Convex Hull Algorithm:}

Andrew’s Algorithm sorts the points and computes the convex hull in two separate chains—lower and upper. The time
complexity is O (n log n), and the space complexity is O(n).


\section{\textbf{Line Segment Algorithms:}}

\subsection{}

\textbf{0.2.6 Algebraic Line Segment Intersection Algorithm:}

The Algebraic method calculates the slopes of the line segments and checks for intersection using algebraic equations.
The time complexity is dependent on the solution of a system of equations and is analyzed further in the results section.

\textbf{0.2.7 CCW Computation Line Segment Intersection Algorithm:}

The CCW (Counter Clockwise) computation method involves determining the orientation of three points. The algorithm checks the orientations of relevant point triplets to identify intersections efficiently.

\textbf{0.2.8 Vector Cross Product Line Segment Intersection Algorithm:}

The Vector Cross Product method utilizes vector operations to determine whether two line segments intersect. This
approach offers an alternative computational perspective.